Reassessing the Role of Theory and Machine Learning in Forecasting Civil Conflict

### 2020-09-26 paper.Rmd
single space

output: 
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
    toc: false
header-includes:
  - \usepackage{floatrow}
  - \floatsetup[figure]{capposition=bottom}
  - \floatsetup[table]{capposition=top}
  - \usepackage[format=plain,labelfont=bf,up]{caption}
  - \usepackage{setspace}\doublespacing
bibliography: "./references.bib"
nocite: |
  @cederman:weidmann:2017
---

>>>>

output: 
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
    toc: false
header-includes:
  - \usepackage{floatrow}
  - \floatsetup[figure]{capposition=bottom}
  - \floatsetup[table]{capposition=top}
  - \usepackage[format=plain,labelfont=bf,up]{caption}
#  - \usepackage{setspace}\doublespacing
bibliography: "./references.bib"
nocite: |
  @cederman:weidmann:2017
---
